Automatically proving equivalence by type-safe reflection

### 2016-02-03 paper-JFP-DTP/content/1-introduction.tex
Minor edits to the paper
Added a reference to the JFP DTP paper

When doing formal certification, we often require equality proofs between
terms.
For example, say we want to certify the function $f\ :\ A \rightarrow
B$. We have two functions $sem_A\ :\ A \rightarrow SEM$ and $sem_B\ : \ B
\rightarrow SEM$ which associate a semantics to each type A
and B. If this semantics describes all of the important properties of
the behaviour of $f$,
then the lemma of correctness of $f$ can be expressed as $forall\ a:A,\ semA\ a =
semB (f\ a)$. Very often, the type $SEM$ has some algebraic
algebraic structure, and it becomes thus possible to
decide equalities in it by following some standard rewriting rules.  
All the equality symbols we have
encountered so far refer to the propositional equality. In the next section,
we will see how this is defined in Idris, and how it differs from the more
primitive judgemental equality.

@@

For
this situation, Idris provides \emph{provisional definitions} with the 
syntax \texttt{?=}. Using a provisional definition here will make
the definition acceptable, but it also generates two proof obligations, one
for each pattern, both of which say that the provided term can be
converted into a term which has the expected type.  For both of these
patterns, it is possible to prove the equality between the expected and
the provided types. These proofs
consist of a series of rewriting steps, where each step uses a property about the
operation $+$ on natural numbers.  For example, the proof for the second
pattern looks like this (with some detail elided):

>>>>

When doing formal certification, we often require equality proofs between
terms.
For example, say we want to certify the function $f\ :\ A \rightarrow
B$. We have two functions $sem_A\ :\ A \rightarrow SEM$ and $sem_B\ : \ B
\rightarrow SEM$ which associate a semantics to each type A
and B. If this semantics describes all of the important properties of
the behaviour of $f$,
then the lemma of correctness of $f$ can be expressed as $forall\ a:A,\ semA\ a =
semB (f\ a)$. This situation happens very often in model transformations where the behaviour of an object has been preserved by some transformations, as for example in the CompCert certified compiler where the original C program and the generated assembly code are proven to have the same operational semantic \cite{Leroy09}.
Very often, the type $SEM$ has some algebraic
algebraic structure, and it becomes thus possible to
decide equalities in it by following some standard rewriting rules.  
All the equality symbols we have
encountered so far refer to the propositional equality. In the next section,
we will see how this is defined in Idris, and how it differs from the more
primitive judgemental equality.

@@

For
this situation, Idris provides \emph{provisional definitions} with the 
syntax \texttt{?=}. Using a provisional definition here will make
the definition acceptable, but it also generates two proof obligations, one
for each pattern, both of which say that the provided term can be
converted into a term which has the expected type.  For both of these
patterns, it is possible to prove the equality between the expected and
the provided types. These proofs
consist of a series of rewriting steps, where each step uses a property about the
operation $+$ on natural numbers.  For example, the proof for the second
pattern is shown in Figure \ref{adc_lemma_2} (with some detail elided):
